Web Service Community \\ Learning

### 2014-06-24 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

>>>>

\begin{itemize}
  \item QoS performance of Web services is highly related to invocation time, since the service status (e.g., workload, number of clients, etc.) and the network environment (e.g., congestion etc.) change over time.
  \item Service users are typically distributed in different geographical locations. The user-observed QoS performance of Web services is greatly influenced by the Internet connections between users and Web services. Different users may observe quite different QoS performance when invoking the same Web service.
\end{itemize}
